A Large-Scale Study of the Use of Eval in R

### 2020-08-25 inst/paper/main.tex
usage metrics

@@

\begin{figure*}[!tb]\centering\includegraphics[width=.9\linewidth]
  {corpus.pdf}\caption{Corpus}\label{fig:corpus}
\end{figure*}

@@

\begin{figure}[!tb]\centering\includegraphics[width=.9\linewidth]
  {programs-code.pdf}\caption{Programs code size}\label{fig:programs-code}
\end{figure}
\begin{figure}[!tb]\centering\includegraphics[width=.9\linewidth]
  {programs-runtime.pdf}\caption{Programs execution time}\label{fig:programs-runtime}
\end{figure}

@@

This section presents an overiew of the usage of \eval in our corpus.
Previous work reported that 82\% of JavaScript-enabled web pages used
\eval~\cite{ecoop11}, the case for R is more striking at \miss{100\%} of the
programs use that feature. In this section, a call to \eval denotes a call
to any one of the functions that provide \eval-like
functionality.\footnote{These include \c{eval}, \c{eval.parent}, \c{evalq}
  and \c{local}.}

This strikingly high number is due to the fact that the language
implementation, the core packages, use \eval extensively. So, in our
analysis, we differentiate \eval based on where they originate from. A {\bf
  core} \eval is one that occurs in the code of a core package.  A {\bf
  dependent} \eval is one that occurs in a package that was included by the
target package. An {\bf own} \eval is one that occurs in the source code of
the target package. We label an \eval occurence as {\bf unknown} when we are
not able to deterimine its origin.\footnote{A source of unknowns is when the
  \eval function is passed as an argument to a function such as \c{lapply},
  another is when the code lacks source references.}

Over all, we observed \AllAllCallCountRnd call to \eval in \CorpusAllProgramsRnd
programs in our corpus. The mean number of calls per run was \miss{20} (with a
min of \miss{1} and a max of \miss{10,000}). Table~\ref{A} details the usage of
\eval across the corpus. The format is T (m/M/x) where T is the total number of
calls observed for all runs of the corpus, m and x are the minimum and maximum
number of calls for any given run, and A is the mean number of calls per run. We
can observe \miss{???}. {\bf <The following is a place holder. Real text will
  come once we have the table.>} The majority of calls come from the core
packages. Kaggle does not have any own calls, any \eval in those happens in
dependent packages and core. Of the \missingNumber packages in our corpus, only
\missingNumber packages call eval.

\begin{verbatim}
Table A

         core      dependent   own
----------------------------------------
CRAN   10M?(1/2/3) 1M?(1/2/3) 1K?(1/2/3)
Kaggle 2K?(1/2/3)  1K?(1/2/3) 0 (0/0/0)
\end{verbatim}

\begin{table}[ht]
  \resizebox{\columnwidth}{!}{%
    \begin{tabular}{r|rrr|}
      \hline
      Source & Core & Dependent & Own \\
      \hline
      CRAN & \CranCoreTotalEvalCallsRnd (\CranCoreMinEvalCallsRnd/\CranCoreAvgEvalCallsRnd/\CranCoreMaxEvalCallsRnd) & \CranDependentTotalEvalCallsRnd (\CranDependentMinEvalCallsRnd/\CranDependentAvgEvalCallsRnd/\CranDependentMaxEvalCallsRnd) & \CranOwnTotalEvalCallsRnd (\CranOwnMinEvalCallsRnd/\CranOwnAvgEvalCallsRnd/\CranOwnMaxEvalCallsRnd) \\
      Kaggle & \KaggleCoreTotalEvalCallsRnd (\KaggleCoreMinEvalCallsRnd/\KaggleCoreAvgEvalCallsRnd/\KaggleCoreMaxEvalCallsRnd) & \KaggleDependentTotalEvalCallsRnd (\KaggleDependentMinEvalCallsRnd/\KaggleDependentAvgEvalCallsRnd/\KaggleDependentMaxEvalCallsRnd) & 0(0/0/0) \\
      \hline
    \end{tabular}
  }
  \label{table:source-eval-summary}
  \caption{Distribution of eval calls in CRAN and Kaggle}
\end{table}

The following table will be replaced. {\bf <At this point separating between
  the different kinds of evals is distracting. We have not argued why it is
  important.>}

\begin{table}[ht]
  \resizebox{\columnwidth}{!}{%
    \begin{tabular}{l|rr|r||rr|r}
      \hline
      \multicolumn{1}{c}{Function}& \multicolumn{3}{c}{Calls} & \multicolumn{3}{c}{Callsites}\\
      \cline{1-1} \cline{2-4} \cline{5-7}
                                  & Core & Packages & Total & Core & Packages & Total\\
      \hline
      \c{eval} & \CoreEvalCallCountRnd & \PackageEvalCallCountRnd  & \AllEvalCallCountRnd & \CoreEvalSiteCountRnd & \PackageEvalSiteCountRnd &  \AllEvalSiteCountRnd\\
      \c{eval.parent} & \CoreEvalParentCallCountRnd & \PackageEvalParentCallCountRnd  & \AllEvalParentCallCountRnd & \CoreEvalParentSiteCountRnd & \PackageEvalParentSiteCountRnd & \AllEvalParentSiteCountRnd\\
      \c{evalq} & \CoreEvalqCallCountRnd & \PackageEvalqCallCountRnd  & \AllEvalqCallCountRnd & \CoreEvalqSiteCountRnd & \PackageEvalqSiteCountRnd & \AllEvalqSiteCountRnd \\
      \c{local} & \CoreLocalCallCountRnd & \PackageLocalCallCountRnd  & \AllLocalCallCountRnd & \CoreLocalSiteCountRnd & \PackageLocalSiteCountRnd & \AllLocalSiteCountRnd \\
      \hline
      Total & \CoreAllCallCountRnd & \PackageAllCallCountRnd  & \AllAllCallCountRnd & \CoreAllSiteCountRnd & \PackageAllSiteCountRnd & \AllAllSiteCountRnd \\
      \hline
    \end{tabular}
  }
  \label{table:eval-count-summary}
  \caption{Distribution of eval calls and callsites in the corpus}
\end{table}

\ref{table:top-ten-package-summary} shows the number of calls to eval
made by the ten most frequent callers to eval. These packages together have
\missingNumber callsites and account for \missingPercentage calls to eval.
Furthermore, the top ten callsites account for \missingPercentage of package
eval calls. A single callsite of \TopTenPackageNameA accounts for over
\missingPercentage calls to eval.

\begin{table}[ht]
  \resizebox{\columnwidth}{!}{%
    \begin{tabular}{l|rrr||l|rrr}
      \hline
      \multicolumn{4}{c}{}& \multicolumn{4}{c}{} \\
      \cline{1-4} \cline{5-8}
      Package & Callsites & Calls & Calls \% & Package & Callsites & Calls & Calls \%\\
      \hline
      \TopTenPackageNameA & \TopTenPackageCallsiteCountA & \TopTenPackageCallCountA &\TopTenPackageCallPercA & \TopTenPackageNameF & \TopTenPackageCallsiteCountF & \TopTenPackageCallCountF & \TopTenPackageCallPercF \\
      \TopTenPackageNameB & \TopTenPackageCallsiteCountB & \TopTenPackageCallCountB &\TopTenPackageCallPercB & \TopTenPackageNameG & \TopTenPackageCallsiteCountG & \TopTenPackageCallCountG & \TopTenPackageCallPercG \\
      \TopTenPackageNameC & \TopTenPackageCallsiteCountC & \TopTenPackageCallCountC &\TopTenPackageCallPercC & \TopTenPackageNameH & \TopTenPackageCallsiteCountH & \TopTenPackageCallCountH & \TopTenPackageCallPercH \\
      \TopTenPackageNameD & \TopTenPackageCallsiteCountD & \TopTenPackageCallCountD &\TopTenPackageCallPercD & \TopTenPackageNameI & \TopTenPackageCallsiteCountI & \TopTenPackageCallCountI & \TopTenPackageCallPercI \\
      \TopTenPackageNameE & \TopTenPackageCallsiteCountE & \TopTenPackageCallCountE &\TopTenPackageCallPercE & \TopTenPackageNameJ & \TopTenPackageCallsiteCountJ & \TopTenPackageCallCountJ & \TopTenPackageCallPercJ \\
      \hline
    \end{tabular}
  }
  \label{table:top-ten-package-summary}
  \caption{Distribution of eval calls and callsites in the top ten packages}
\end{table}

\missingGraph shows the distribution of number of callsites to eval across these
packages. \missingNumber packages have a single eval callsite.

\begin{table}[ht]
  \resizebox{\columnwidth}{!}{%
    \begin{tabular}{rr|rr|rr}
      \hline
      Callsites & Packages & Callsites & Packages & Callsites & Packages \\
      \hline
      \SiteSummarySiteCountA & \SiteSummaryPackageCountA & \SiteSummarySiteCountF & \SiteSummaryPackageCountF & \SiteSummarySiteCountK & \SiteSummaryPackageCountK \\
      \SiteSummarySiteCountB & \SiteSummaryPackageCountB & \SiteSummarySiteCountG & \SiteSummaryPackageCountG & \SiteSummarySiteCountL & \SiteSummaryPackageCountL \\
      \SiteSummarySiteCountC & \SiteSummaryPackageCountC & \SiteSummarySiteCountH & \SiteSummaryPackageCountH & \SiteSummarySiteCountM & \SiteSummaryPackageCountM \\
      \SiteSummarySiteCountD & \SiteSummaryPackageCountD & \SiteSummarySiteCountI & \SiteSummaryPackageCountI & \SiteSummarySiteCountN & \SiteSummaryPackageCountN \\
      \SiteSummarySiteCountE & \SiteSummaryPackageCountE & \SiteSummarySiteCountJ & \SiteSummaryPackageCountJ & \SiteSummarySiteCountO & \SiteSummaryPackageCountO \\ 
      \hline
    \end{tabular}
  }
  \label{table:site-package-summary}
  \caption{Distribution of callsites across packages}
\end{table}

\subsubsection{The size of \eval}

>>>>

\begin{figure*}[!tb]\centering\includegraphics[width=.8\linewidth]
  {corpus.pdf}\caption{Corpus}\label{fig:corpus}
\end{figure*}

@@

\begin{figure}[!htb]\centering\includegraphics[width=.9\linewidth]
  {programs-code.pdf}\caption{Programs code size}\label{fig:programs-code}
\end{figure}

\begin{figure}[!htb]\centering\includegraphics[width=.9\linewidth]
  {programs-runtime.pdf}\caption{Programs execution time}\label{fig:programs-runtime}
\end{figure}

@@

@@

This section presents an overiew of the usage of \eval in our corpus.
Previous work reported that 82\% of JavaScript-enabled web pages used
\eval~\cite{ecoop11}. The case for R is more striking with 100\% of the
programs using that \eval.\footnote{In this section, we combine calls to
  \c{eval}, \c{eval.parent}, \c{evalq} and \c{local}.}  This high number is
explained by the fact that the R implementation, its core packages, use
\eval extensively. In our analysis, we differentiate uses of \eval based on
where they originate from. A {\bf core} \eval is one that occurs in the code
of a core package.  A {\bf dependent} \eval is one that occurs in a package
that was included by the target package. An {\bf own} \eval is one that
occurs in the source code of the target package.

Over all, we observed \AllAllCallCountRnd calls to \eval in the
\CorpusAllProgramsRnd programs in our corpus.  Table~\ref{A} details this
run-time information. The format is T (m/M/x) where T is the total number of
calls observed for all runs of the corpus, m and x are the minimum and
maximum number of calls for any given run, and M is the mean number of calls
per run. We can observe that an average run of CRAN package will trigger 581
{\eval}s in core package, 532 in dependent packages and 292 in the package
itself.  The Kaggle data set has small programs, and, these programs only
trigger \eval in core and dependent packages. Thus, an average Kaggle run
has 412 core calls, 96 dependent calls, and no own calls.

\begin{table}[ht]
\resizebox{\columnwidth}{!}{%
\begin{tabular}{@{}r|ccc@{}} \hline
Source & Core & Dependent & Own \\\hline
      %      CRAN & \CranCoreTotalEvalCallsRnd (\CranCoreMinEvalCallsRnd/\CranCoreAvgEvalCallsRnd/\CranCoreMaxEvalCallsRnd) & \CranDependentTotalEvalCallsRnd (\CranDependentMinEvalCallsRnd/\CranDependentAvgEvalCallsRnd/\CranDependentMaxEvalCallsRnd) & \CranOwnTotalEvalCallsRnd (\CranOwnMinEvalCallsRnd/\CranOwnAvgEvalCallsRnd/\CranOwnMaxEvalCallsRnd) \\
CRAN & \CranCoreTotalEvalCallsRnd (1 / 581 / 416K)  & \CranDependentTotalEvalCallsRnd (1 / 532 / 183K) & \CranOwnTotalEvalCallsRnd (1 / 292 / 144K)\\
Kaggle & \KaggleCoreTotalEvalCallsRnd (1 / 412 / 2.8K) & \KaggleDependentTotalEvalCallsRnd (3 / 96 / 1.1K) & 0 (0 / 0 / 0) \\
%      Kaggle & \KaggleCoreTotalEvalCallsRnd (\KaggleCoreMinEvalCallsRnd/\KaggleCoreAvgEvalCallsRnd/\KaggleCoreMaxEvalCallsRnd) & \KaggleDependentTotalEvalCallsRnd (\KaggleDependentMinEvalCallsRnd/\KaggleDependentAvgEvalCallsRnd/\KaggleDependentMaxEvalCallsRnd) & 0(0/0/0) \\
      \hline
    \end{tabular}
  }
  \label{A}
  \caption{Eval calls in CRAN and Kaggle}
\end{table}

%% The following table will be replaced. {\bf <At this point separating between
%%   the different kinds of evals is distracting. We have not argued why it is
%%   important.>}

%% \begin{table}[ht]\resizebox{\columnwidth}{!}{\begin{tabular}{l|rr|r||rr|r}\hline
%% \multicolumn{1}{c}{Function}& \multicolumn{3}{c}{Calls} & \multicolumn{3}{c}{Callsites}\\
%% \cline{1-1} \cline{2-4} \cline{5-7}
%% & Core & Packages & Total & Core & Packages & Total\\\hline
%% \c{eval} & \CoreEvalCallCountRnd & \PackageEvalCallCountRnd  & \AllEvalCallCountRnd & \CoreEvalSiteCountRnd & \PackageEvalSiteCountRnd &  \AllEvalSiteCountRnd\\
%% \c{eval.parent} & \CoreEvalParentCallCountRnd & \PackageEvalParentCallCountRnd  & \AllEvalParentCallCountRnd & \CoreEvalParentSiteCountRnd & \PackageEvalParentSiteCountRnd & \AllEvalParentSiteCountRnd\\
%% \c{evalq} & \CoreEvalqCallCountRnd & \PackageEvalqCallCountRnd  & \AllEvalqCallCountRnd & \CoreEvalqSiteCountRnd & \PackageEvalqSiteCountRnd & \AllEvalqSiteCountRnd \\
%% \c{local} & \CoreLocalCallCountRnd & \PackageLocalCallCountRnd  & \AllLocalCallCountRnd & \CoreLocalSiteCountRnd & \PackageLocalSiteCountRnd & \AllLocalSiteCountRnd \\\hline
%% Total & \CoreAllCallCountRnd & \PackageAllCallCountRnd  & \AllAllCallCountRnd & \CoreAllSiteCountRnd & \PackageAllSiteCountRnd & \AllAllSiteCountRnd \\  \hline
%% \end{tabular} } \label{table:eval-count-summary}
%%  \caption{Distribution of eval calls and callsites in the corpus}
%% \end{table}

%% \ref{table:top-ten-package-summary} shows the number of calls to eval
%% made by the ten most frequent callers to eval. These packages together have
%% \missingNumber callsites and account for \missingPercentage calls to eval.
%% Furthermore, the top ten callsites account for \missingPercentage of package
%% eval calls. A single callsite of \TopTenPackageNameA accounts for over
%% \missingPercentage calls to eval.

%% \begin{table}[ht]
%%   \resizebox{\columnwidth}{!}{%
%%     \begin{tabular}{l|rrr||l|rrr}
%%       \hline
%%       \multicolumn{4}{c}{}& \multicolumn{4}{c}{} \\
%%       \cline{1-4} \cline{5-8}
%%       Package & Callsites & Calls & Calls \% & Package & Callsites & Calls & Calls \%\\
%%       \hline
%%       \TopTenPackageNameA & \TopTenPackageCallsiteCountA & \TopTenPackageCallCountA &\TopTenPackageCallPercA & \TopTenPackageNameF & \TopTenPackageCallsiteCountF & \TopTenPackageCallCountF & \TopTenPackageCallPercF \\
%%       \TopTenPackageNameB & \TopTenPackageCallsiteCountB & \TopTenPackageCallCountB &\TopTenPackageCallPercB & \TopTenPackageNameG & \TopTenPackageCallsiteCountG & \TopTenPackageCallCountG & \TopTenPackageCallPercG \\
%%       \TopTenPackageNameC & \TopTenPackageCallsiteCountC & \TopTenPackageCallCountC &\TopTenPackageCallPercC & \TopTenPackageNameH & \TopTenPackageCallsiteCountH & \TopTenPackageCallCountH & \TopTenPackageCallPercH \\
%%       \TopTenPackageNameD & \TopTenPackageCallsiteCountD & \TopTenPackageCallCountD &\TopTenPackageCallPercD & \TopTenPackageNameI & \TopTenPackageCallsiteCountI & \TopTenPackageCallCountI & \TopTenPackageCallPercI \\
%%       \TopTenPackageNameE & \TopTenPackageCallsiteCountE & \TopTenPackageCallCountE &\TopTenPackageCallPercE & \TopTenPackageNameJ & \TopTenPackageCallsiteCountJ & \TopTenPackageCallCountJ & \TopTenPackageCallPercJ \\
%%       \hline
%%     \end{tabular}
%%   }
%%   \label{table:top-ten-package-summary}
%%   \caption{Distribution of eval calls and callsites in the top ten packages}
%% \end{table}

Table \ref{table:site-package-summary} shows the results of static analysis
for the CRAN packages in our corpus. 89 packages have a single call site,
and one package has \miss{252} call sites of \eval. \miss{XXX} packages have
no calls to \eval. The core packages have \miss{41} callsites of eval and
Kaggle has none. These static numbers are under approximations as \eval may
be called reflectively, through aliases, or passed to a higher-order function.

\begin{table}[ht]\resizebox{\columnwidth}{!}{%
\begin{tabular}{rr|rr|rr}\hline
Callsites & Packages & Callsites & Packages & Callsites & Packages \\ \hline
\SiteSummarySiteCountA & \SiteSummaryPackageCountA & \SiteSummarySiteCountF & \SiteSummaryPackageCountF & \SiteSummarySiteCountK & \SiteSummaryPackageCountK \\
\SiteSummarySiteCountB & \SiteSummaryPackageCountB & \SiteSummarySiteCountG & \SiteSummaryPackageCountG & \SiteSummarySiteCountL & \SiteSummaryPackageCountL \\
\SiteSummarySiteCountC & \SiteSummaryPackageCountC & \SiteSummarySiteCountH & \SiteSummaryPackageCountH & \SiteSummarySiteCountM & \SiteSummaryPackageCountM \\
\SiteSummarySiteCountD & \SiteSummaryPackageCountD & \SiteSummarySiteCountI & \SiteSummaryPackageCountI & \SiteSummarySiteCountN & \SiteSummaryPackageCountN \\
      \SiteSummarySiteCountE & \SiteSummaryPackageCountE & \SiteSummarySiteCountJ & \SiteSummaryPackageCountJ & \SiteSummarySiteCountO & \SiteSummaryPackageCountO \\    \hline
\end{tabular}} \label{table:site-package-summary}
\caption{Distribution of callsites in CRAN}
\end{table}
